---
output: md_document
---
[![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)](https://github.com/orangemug/stability-badges)


# Gulf of St. Lawrence Ecosystem Approach package

This package offers a database of measured variables which can inform an ecosystem approach for the Gulf of St. Lawrence, Canada. In addition to a dataset at the ecoregion level, standard query functions are provided to extract relevant data series.

This package is intentionally kept small and aggregated to facilitate analyses that call it without breaking existing analyses that depend on it and to feed other analyses with only limited need to look at the guts of this package. The package does not provide data at a sample by sample level but always integrated to the ecoregion level. If you would like to have finer scale data it is suggested that you first consult the references in the dataset help files and then the individual responsble for that data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install, eval=FALSE}
devtools::install_github(https://github.com/duplisea/gslea)
library(gslea)
```

```{r loadlibrary, include=FALSE}
library(gslea)
```


## State of development

This database presently includes physical oceanographic and biological oceanographic data for the Gulf Ecoregions.

## Map of the Gulf of St Lawrence with Ecoregions and fish survey stations

```{r gslmap.plain, eval=TRUE,include=FALSE}
gslea.map.f(bathymetry=F)
```

## Data available

Presently, gslea includes physical oceanographic, chemical oceanographic, planktonic and phenological data. These data are stored as a data.table called EA.data which is a long format table with one row per observation and which enables an efficient data extraction that can enable other analyses. Auxially datasets for mapping such as bathymetry are also included and descriptive table describing the ecosystem measured variables.

## Extracting data


```{r dataextraction, eval=TRUE}


```

# a scatterplot of all the different environmental variables

```{r scatterplot}

```


## State of development
GSL data by ecoregions in available. A standard data extraction function is being developed.

### Project particpants

Hugues Benoît, Daniel Duplisea, Peter Galbraith, David Merette, Stéphane Plourde, Marie-Julie Roux, Bernard Sainte-Marie
