---
output: md_document
---
[![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)](https://github.com/orangemug/stability-badges)

**This package is currently unverfied and incomplete and should not be used for any analysis at present**


# Gulf of St. Lawrence Ecosystem Approach

This package is under development. It is intended to offer data and tools for analysis of the Gulf of St. Lawrence ecosystem which should aid in an ecosystem approach to fisheries.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install, eval=FALSE}
devtools::install_github(https://github.com/iml-assess/gslea)
library(gslea)
```

## State of development

Functions in this package are placeholders at present. Please see the following for some of the planned functions that will be included in the package.

https://github.com/duplisea/gslea/Candidate_ecological_indicators_for_EGSL_mjr.html

Some functionality is presently available through gslea's dependent package "size":

https://github.com/duplisea/size/


Please check back for progress

### Present project contributors

Hugues Benoît, Daniel Duplisea, Peter Galbraith, David Merette, Stéphane Plourde, Marie-Julie Roux, Bernard Sainte-Marie
